%%%%% Pair comparison algorithm
\begin{algorithm}
\caption{Pair comparison}\label{pair-comp}
  \begin{algorithmic}
    \Procedure{PairComparison}{$revids$}
    \For {$ i \gets 0, $length($revids$)}
    \If{pair distance not already in database}
    \State $str1 \gets $\LineIf{``"}{$i=0$}{database.gettext($revs[i-1]$)}
    \State $str2 \gets $database.gettext($revs[i]$)
    \State $dist \gets $PairDistance($str1, str2$)\Comment{See algorithm~\ref{dist-calc}}
    \State databaseinsert.pairdistanceinsert($dist$)  
    \EndIf
    \EndFor
  \EndProcedure
  \end{algorithmic}
\end{algorithm}

The interest, instead, is in exactly how we calculate this
distance. We discussed earlier that we would use native WikiMarkup
tags in order to identify different `species' of text. By doing so, we
could characterise a single revision in terms of the kinds of text
dealt in. By characterising an edit with a series of different edit
difference we also perhaps create the opportunity to consider some as
more valuable than others.\label{multiprocessing-bit}

The algorithm that was settled upon left the levenshtein calculator
itself naive of text species -- instead we simply split the text up
and calculate levenstein distance separately. We traverse each string
from beginning to end, using simple regex expressions to identify and
extract different kinds of text, and calculating the levenshtein
distance for each separately. This process is detailed in
algorithm~\ref{dist-calc}. 

%%%%% Distance calculation procedure
\begin{algorithm}
  \caption{Revision pair distance calculation}\label{dist-calc}
  \begin{algorithmic}
    \State $regexes \gets $\{
    \Statex \tab`math1': `$<$math$>$((?!$<${\textbackslash}/math$>$).)*$<${\textbackslash}/math$>${\textbackslash}S',
    \Statex \tab`math2': `\{\{math((?!\}\}).)*\}\}',
    \Statex \tab`bquote': `$<$blockquote$>$((?!$<${\textbackslash}/blockquote$>$).)*$<${\textbackslash}/blockquote$>${\textbackslash}S'
    \Statex  \tab...
    \Statex\}\Comment{Regexes that recognise single Wikimarkup tags}
    \State $reggroups \gets $\{\label{dist-calc-groups}
    \Statex  \tab`maths':(regexes[`math1'], regexes[`math2']),
    \Statex  \tab...
    \Statex \}\Comment{Group of regexes by 'species'}
    \State $distances \gets \emptyset$
    \Function{PairDistance}{$str1,str2$}
    \State $strs \gets [str1, str2]$
    \ForAll {$key, reg \in reggroups$}
    \State $comparestr \gets [``", ``"]$
    \For {$i \gets 0,1$}
    \State $matches \gets reg.matches(strs[i])$
    \ForAll {$m \in matches$}
    \State $match, strs[i] \gets $extractsplit($m.start, m.end, strs[i]$)
    \State $comparestr[i] \gets comparestr[i] + match$
    \EndFor
    \EndFor
    \If {length($comparestr[0]$)$ > 0$ OR length($comparestr[1]$)$ > 0$}
    \State $distances[key] \gets LevDist(comparestr[0], comparestr[1])$ \Comment{See algorithm~\ref{lev-dist}}
    \Else
    \State $distances[key] \gets 0$
    \EndIf
    \EndFor
    \State $distances[$`$norm$'$] \gets LevDist(strs[0], strs[1])$
    \Comment{Process the remainder}
    \State return $distances$
    \EndFunction
  \end{algorithmic}
\end{algorithm}

In practice, this algorithm was much quicker than trying to add an
awareness of text species to the levenshtein calculator itself. We
using regex statements, we can search and split the string relatively
quickly, and use this preprocessing to alleviate the levenshtein
distance calculator of the burden of being aware of the kinds of text
it is dealing with. With this awareness integrated, because
levenshtein distance considers one character at a time, these
operations of flagging and identifying areas of text were inevitably
multiplied many thousands of time in one operation. Instead we were
able to use a fairly simply algorithm for calculating levenshtein
distance, found in algorithm~\ref{lev-dist}.

We will discuss different levenshtein-related algorithms further on
this thesis, but for now we can say that the one we reference here is
fairly basic, but with an optimised space efficiency. We see that we
don't hold a whole matrix for the two strings, only the current and
previous row. We may also describe the PairDistance overall as a
divide-and-conquer algorithm. It improves the space complexity of the
algorithm a little, and allows us the employ parallel or threaded
processing in order to improve efficiency of computation.

\begin{algorithm}
  \begin{algorithmic}
    \Function{LevDist}{$str1, str2$}
    \State $s1len \gets $length($str1$)
    \State $s2len \gets $length($str2$)
    \State $column \gets [0_{1}, 0_{2}, \ldots, 0_{s1len}]$
    \For{$x \gets 1,s2len$}
    \State $col[x] \gets x$
    \EndFor
    \For{$p \gets 1,s1len$}
    \State $column[0] \gets p$
    \State $r \gets p-1$
    \For{$q \gets 1,s2len$}
    \State $oldnum \gets column[q]$
    \State $column[q] \gets min(col[q]+1, col[q-1] + 1, r + str1[p-1] \neq str2[q-1])$
    \EndFor
    \EndFor
    \State return $col[s1len]$
    \EndFunction
  \end{algorithmic}
  \caption{Levenshtein distance calculator}
  \label{lev-dist}
\end{algorithm}

Our procedure for collecting these values is described in
algorithm~\ref{traj-calc}.

%%%%% Trace trajectory algorithm
\begin{algorithm}
\caption{Page trajectory calculation}\label{traj-calc}
  \begin{algorithmic}
    \Procedure{TrajectoryCalculation}{$revids, domain$}
    \State $target \gets $database.gettext($revids[-1]$)\Comment{Last revision in list is most recent}
    \For {$i \gets length(revids), 0$}
    \If{trajectory distance not already in database}
    \State $str1 \gets $database.gettext($revids[i]$)
    \State $dist \gets $LevDist($str1, target$)\Comment{See algorithm~\ref{lev-dist}}
    \State $database.inserttrajectoryinsert(dist)$    
    \EndIf
    \EndFor
    \For{$i \gets 0, length(revids)$}
    \State $dist2 \gets $database.gettrajectory($revids[i],domain$)
    \State $dist1 \gets$
        \LineIf{database.gettrajectory($revid[i-1],domain$)}{$i \neq 0$}{$2
          \times disty$}
    \State $time2 \gets $database.gettimestamp($revid[i],domain$)
    \State $time1 \gets $
        \LineIf{database.gettimestamp($revid[i-1],domain$)}{$i \neq 0$}{$timex$} 
    \State ${\Delta}x \gets time2 - time1$
    \State ${\Delta}y \gets dist2 - dist1$
    \If{${\Delta}x > 0$}
    \State $gradient = \frac{arctan({\Delta}y/{\Delta}x)}{\pi}$ 
    \ElsIf{$x = 0$}
    \State $gradient = $\LineIf{1}{$y < 0$}{0}
    \EndIf
    \State database.insertgradient($revid[i],domain,gradient$)
    \EndFor
    \EndProcedure
  \end{algorithmic}
\end{algorithm}
